Pillar 2 - Topic Modeling

### 2019-02-26 Pillar 2 - Topic Modeling.Rmd
commenting section on LDA.

# Setup
```{r import data}
load("output/data_pillar_2.RDATA")

@@

# TF-IDF
## Functions for Generating Barplots and Word Clouds

```{r compute_tf_idf, cache = TRUE}
compute_tf_idf <- function(data){

@@

```{r plot_tf_idf}
plot_tf_idf <- function(data, n_col = 5, id_plot = NULL){

@@

## Course Level
```{r tf-idf course, cache = TRUE}
prepare_tf_idf_course <- function(data){

@@

# LDA

```{r my_cast_tdm}
my_cast_tdm <- function(data, level) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

@@

## Ideal Number of Topics (RUN ON UM COMPUTER)

```{r}
my_control <- list(

@@

)
```

```{r}
my_FindTopicsNumber <- function(data_cast, n_topics){

@@

```{r}
start.time <- Sys.time()

@@

```{r}
start.time <- Sys.time()

>>>>

# Setup
We load the environment `output/data_pillar_2.RDATA`. It contains the data sets:
`d_AoD`, `d_assessment`, `d_course`, `d_description`, `d_manual`, `d_overview`, `d_transcript`, and a list `lists`.
For `d_description` and `d_overview`, we keep only the most recent year.
```{r import data}
load("output/data_pillar_2.RDATA")

@@

# TF-IDF
## Functions for Generating Barplots and Word Clouds
The function `compute_tf_idf` computes the inverse term document frequency, we apply `compute_tf_idf` on descriptions, overviews and manuals. 
```{r compute_tf_idf, cache = TRUE}
compute_tf_idf <- function(data){

@@

The function `plot_tf_idf` plots a bar-graph of the most important words for each level of granularity and  their corresponding word clouds. 
```{r plot_tf_idf}
plot_tf_idf <- function(data, n_col = 5, id_plot = NULL){

@@

## Course Level
The function `prepare_tf_idf_course` selects 25 random courses, the top ten words with highest tf_idf, and finally renames a facet to 'Course ID').
We apply the function to `id_plot` and pipe it to produce graphs.
```{r tf-idf course, cache = TRUE}
prepare_tf_idf_course <- function(data){

@@

# LDA
The function `my_cast_tdm` casts our dataframes into a tdm.
```{r my_cast_tdm}
my_cast_tdm <- function(data, level) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

@@

## Ideal Number of Topics (RUN ON UM COMPUTER)
To decide the number of topics to discover, we run (four) three different tests.

First we set the control for the test.
```{r controls}
my_control <- list(

@@

)
```
The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 
```{r function my_FindTopicsNumber }
my_FindTopicsNumber <- function(data_cast, n_topics){

@@

}
```
We run the test for descriptions, documenting the duration (starting_time - ending_time). We build 95 models (5 to 100 in increments of 1).
```{r description topics, cache = TRUE}
start.time <- Sys.time()

@@

We run the test for overview, documeting its duration. 
```{r overview topics, cache = TRUE}
start.time <- Sys.time()
